# Desarrollo Prueba 2

```{r}
# librerías
pacman::p_load(dplyr, sjPlot, sjmisc)
sessionInfo()
```


```{r, include=FALSE}
load(url("https://github.com/cursos-metodos-facso/datos-ejemplos/raw/refs/heads/main/dataset1.RData"))
load(url("https://github.com/cursos-metodos-facso/datos-ejemplos/raw/refs/heads/main/dataset2.RData"))
load(url("https://github.com/cursos-metodos-facso/datos-ejemplos/raw/refs/heads/main/dataset3.RData"))
load(url("https://github.com/cursos-metodos-facso/datos-ejemplos/raw/refs/heads/main/dataset4.RData"))
```

# Revisar

```{r}
# Revisar
sjmisc::frq(dataset1$autoritarismo)
sjmisc::frq(dataset2$autoritarismo)
sjmisc::frq(dataset3$autoritarismo)
sjmisc::frq(dataset4$autoritarismo)

sjmisc::frq(dataset1$ingresos)
sjmisc::frq(dataset2$ingresos)
sjmisc::frq(dataset3$ingresos)
sjmisc::frq(dataset4$ingresos)

sjmisc::frq(dataset1$ingresos_rec)
sjmisc::frq(dataset2$ingresos_rec)
sjmisc::frq(dataset3$ingresos_rec)
sjmisc::frq(dataset4$ingresos_rec)

sjmisc::frq(dataset1$educ_rec)
sjmisc::frq(dataset2$educ_rec)
sjmisc::frq(dataset3$educ_rec)
sjmisc::frq(dataset4$educ_rec)

# Codigo de respuesta a preguntas
# dataset1
cor.test(dataset1$ingresos, dataset1$autoritarismo, complete.obs = TRUE, method = "pearson")
sjPlot::plot_scatter(data = dataset1, x = ingresos, y = autoritarismo)

cormat <- dataset1 %>% 
  dplyr::select(educ_rec, autoritarismo, ingresos)
sjPlot::tab_corr(cormat, 
                 na.deletion = "pairwise", # espeficicamos tratamiento NA
                 triangle = "lower")

chisq.test(dataset1$educ_rec, dataset1$ingresos_rec)

# dataset2
cor.test(dataset2$ingresos, dataset2$autoritarismo, complete.obs = TRUE, method = "pearson")
sjPlot::plot_scatter(data = dataset2, x = ingresos, y = autoritarismo)


cormat <- dataset2 %>% 
  dplyr::select(educ_rec, autoritarismo, ingresos)
sjPlot::tab_corr(cormat, 
                 na.deletion = "pairwise", # espeficicamos tratamiento NA
                 triangle = "lower")


chisq.test(dataset2$educ_rec, dataset2$ingresos_rec)


# dataset3
cor.test(dataset3$ingresos, dataset3$autoritarismo, complete.obs = TRUE, method = "pearson")
sjPlot::plot_scatter(data = dataset3, x = ingresos, y = autoritarismo)


cormat <- dataset3 %>% 
  dplyr::select(educ_rec, autoritarismo, ingresos)
sjPlot::tab_corr(cormat, 
                 na.deletion = "pairwise", # espeficicamos tratamiento NA
                 triangle = "lower")


chisq.test(dataset3$educ_rec, dataset3$ingresos_rec)


# dataset4
cor.test(dataset4$ingresos, dataset4$autoritarismo, complete.obs = TRUE, method = "pearson")
sjPlot::plot_scatter(data = dataset4, x = ingresos, y = autoritarismo)

cormat <- dataset4 %>% 
  dplyr::select(educ_rec, autoritarismo, ingresos)
sjPlot::tab_corr(cormat, 
                 na.deletion = "pairwise", # espeficicamos tratamiento NA
                 triangle = "lower")

chisq.test(dataset4$educ_rec, dataset4$ingresos_rec)



